### 2014-03-02 paper/extensions.tex
non-deterministic langs

Despite allowing a number of practical schedulers to be expressed, our
scheduler parametrization is limited.
%
For instance, since |alpha| is a map on task lists, schedulers that
rely on the global state |iS| or previous task configurations cannot
be expressed.
%
Though, we do not believe this to be a fundamental limitation, our
current formalization cannot directly be applied to more-powerful, but
safe, scheduling policies, as considered in~\tocite{}.
%
More fundamentally, our definitions rely on deterministic relations,
and thus extending the system to consider non-deterministic schedulers
is non-trivial.
%
For instance, this may potentially require the security condition to
consider \emph{low-determinism}, which states that a program is secure
only if |l|-equivalent results are deterministic~\tocite{}. %both andrei and steve's papers

@@

\subsection{Other target languages}

Non-deterministic reduction.

\cut{

The good thing about our approach is that we are indifferent to the
functionality implemented in the IFC language: as long as you can
prove termination sensitive non-interference with the IFC language
\Red{What is the IFC language? Make sure it is written down}, you
can combine it with another target language.  In this section,
we briefly review various extensions you can make to the base IFC
language to provide IFC-aware versions of target language features.

}

>>>>

Despite allowing a number of practical schedulers to be expressed, our
scheduler parametrization is limited.
%
For instance, since |alpha| is a map on task lists, schedulers that
rely on the global state |iS| or previous task configurations cannot
be expressed.
%
Though, we do not believe this to be a fundamental limitation, our
current formalization cannot directly be applied to more-powerful, but
safe, scheduling policies, as considered in~\tocite{}.
%
More fundamentally, our definitions rely on deterministic relations,
and thus extending the system to consider non-deterministic schedulers
(or even non-deterministic target languages) is non-trivial.
%
For instance, this may potentially require the security condition to
consider \emph{low-determinism}, which states that a program is secure
only if |l|-equivalent results are deterministic~\tocite{}. %both andrei and steve's papers

@@
